\papertitle

### 2025-03-20 src/tex/ms.tex

\begin{abstract}
Calculation of the centre of mass of a group of particles in a periodically-repeating cell is an important aspect of chemical and physical simulation. 
One popular approach, described by Bai and Breen, calculates the centre of mass via the projection of the individual particles' coordinates onto a circle.
This approach, which is mathematically equivalent to finding the first moment of the Fourier series of the mass density, suffers from some numerical error. 
Here, we discuss this inaccuracy and propose an extension that overcomes it, enabling improved accuracy across computational simulation. 
\end{abstract}

>>>>

\begin{abstract}
Calculation of the centre of mass of a group of particles in a periodically-repeating cell is an important aspect of chemical and physical simulation. 
One popular approach calculates the centre of mass via the projection of the individual particles' coordinates onto a circle [Bai \& Breen, \emph{J. Graph. Tools} \textbf{13}(4), 53, (2008)].
This approach, which is mathematically equivalent to finding the first moment of the Fourier series of the mass density, suffers from some numerical error. 
Here, we discuss this inaccuracy and propose an extension that overcomes it, enabling improved accuracy across computational simulation. 
\end{abstract}
